---
title: "Loss Distribution - 6/30/16 Portfolio"
output: word_document
date: "August 2, 2016"
---

```{r setup, include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
options(digits = 1, scipen = 9)
  wd_out <- paste("C:/Box Sync/Risk Appetite - Provisioning Project/",
            "Working Folders for RAP Modules/Stress Testing/Loss Distribution Simulation",
            "/output",
            sep="")
  setwd(wd_out)
load('loss_sim_08.02.16.Rdata')
```


### Underlying and assumptions

* repeated simulation of loss, based on probability of default as independent uniform random variable
* `r active_date` portfolio
* pds taking in to account risk category
* `r n_missing_pd` loans with `r m$balance_missing_pd / 1e6`M in current given pds imputed
* `r m$balance / 1e6`M balance
* `r m$max_loan_loss/1e6`M max exposure (max loss)
* `r median(pds) * 100`% median pd, `r mean(pds) * 100`% average
* collateral reduces lgd by ~20%
* risk category affects ead (`r ead$current` for current, `r ead$special_mention` and higher for non-current)

### Result

##### Loss Distribution

```{r echo=FALSE}
p.dist
```

Loss rate and amount by percentile (below, and indicated by vertical lines in above):
```{r echo=FALSE}
options(digits = 2)
quant_table
```

Expected Loss (pd * ead * lgd * (1 - guarantee)), as amount, percentage of total balance, the median pd, and the exposure (ie the most that could be lost given assumptions):

```{r echo=FALSE}
cat_table[,1:4]
cat_table[,c(1,5:6)]
```

Due to assumptions about guarantees, collateral, and exposure at default, `r m$max_loan_loss/1e6`M is the maximum loss amount, on the `r m$balance/1e6`M portfolio.
